Bird beak's elaboration and innovation

### 2023-05-30 Analysis/06-Figure_with_correlations.Rmd
Update 06-Figure_with_correlations.Rmd

## Calculate the correlations for the projections onto the group' axes
super_group_cor <- get.correlations.plot(results$super_results_within, exclude.phylo = TRUE)
```

@@

```{r, echo = TRUE, eval = TRUE}
## Get all the correlations for all the clades
cor_mega_level <- get.correlations.scores(results$super_results_phylo)
cor_macro_level <- get.correlations.scores(results$super_results_within)

@@

## Plot the correlations
pdf("../Manuscript/Figures/correlations_fable.pdf")
par(mfrow = c(1,2))
par(mar = c(5, 8, 4, 0) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_mega_level, col = super_orders_col,
                y.axis = TRUE, plot.phylo = TRUE,
                main = "Species projected onto\nthe whole phylogeny VCV") 
par(mar = c(5, 2, 4, 6) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_macro_level, col = super_orders_col,
                y.axis = FALSE, plot.phylo = FALSE,
                main = "Species projected onto\ntheir superorders' VCV")
dev.off()
```

@@

## Plotting each individual correlation plots
for(i in 1:8) {
    par(mar = c(2,2.5,2,1.5))
    plot.correlations(super_group_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter, with.quadrant = FALSE, contour = NULL)
}
dev.off()
```

>>>>

## Calculate the correlations for the projections onto the group' axes
super_group_cor <- get.correlations.plot(results$super_results_within, exclude.phylo = TRUE)

## Check for order_results_within
order_correlations <- get.correlations.plot(results$order_results_within, exclude.phylo = TRUE)
```

@@

```{r, echo = TRUE, eval = TRUE}
## Get all the correlations for all the clades
cor_mega_super_orders <- get.correlations.scores(results$super_results_phylo)
cor_macro_super_orders <- get.correlations.scores(results$super_results_within)
cor_macro_orders <- get.correlations.scores(results$order_results_within)

@@

## Plot the correlations
pdf("../Manuscript/Figures/correlations_fable_super_orders.pdf")
par(mfrow = c(1,2))
par(mar = c(5, 8, 4, 0) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_mega_super_orders, col = super_orders_col,
                y.axis = TRUE, plot.phylo = TRUE,
                main = "Species projected onto\nthe whole phylogeny major axes") 
par(mar = c(5, 2, 4, 6) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_macro_super_orders, col = super_orders_col,
                y.axis = FALSE, plot.phylo = FALSE,
                main = "Species projected onto\ntheir superorders' major axes")
dev.off()

## Correlation fable
pdf(width = 5, height = 9, file = "../Manuscript/Figures/correlations_fable_orders.pdf")
load("../Data/Processed/tip_colours_orders.rda")
orders_col <- c(tip_colours_orders, "phylogeny" = "grey")
orders_col[] <- "black"
par(mar = c(5, 8, 4, 0) + 0.1, bty = "n") # c(bottom, left, top, right)
plot.cor.scores(cor_macro_orders, col = orders_col,
                y.axis = TRUE, plot.phylo = FALSE,
                show.phylo = FALSE, xlim = c(-0.5, 1),
                main = "Species projected onto\ntheir orders' major axes") 
dev.off()
```

@@

## Plotting each individual correlation plots
for(i in 1:8) {
    par(mar = c(2,2.5,2,1.5))
    plot.correlations(super_group_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter, with.quadrant = FALSE, contour = NULL)
}
dev.off()

## Extra figure
pdf("../Manuscript/Figures/correlations_2.pdf", height = 20/3*1.3, width = 8*1.3)
par(mfrow = c(5,6))
for(i in 1:26) {
    par(mar = c(2,4,2.5,0)+0.1)
    plot.correlations(order_correlations[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter, with.quadrant = FALSE, contour = NULL)
}
dev.off()
```
